Excuse me, do you have a moment to talk about version control?

### 2017-10-05 README.Rmd
Add missing open paren

Many people who don't use Git unwittingly re-invent a poor man's version of it. Figure \ref{fig:diy-vs-git} depicts a hypothetical analysis of the iris data, captured in a single R source file. With informal version control, contributors create derivative copies of `iris.R`, decorating the file name with initials, dates, and other descriptors. Even when working alone, this leads to multiple versions of `iris.R` of indeterminate relatedness (Figure \ref{fig:diy-vs-git}A). In collaborative settings based on email distribution, the original file swiftly becomes part of a complicated phylogeny that no amount of "Track changes" and good intentions can resolve Figure \ref{fig:diy-vs-git}B).

>>>>

Many people who don't use Git unwittingly re-invent a poor man's version of it. Figure \ref{fig:diy-vs-git} depicts a hypothetical analysis of the iris data, captured in a single R source file. With informal version control, contributors create derivative copies of `iris.R`, decorating the file name with initials, dates, and other descriptors. Even when working alone, this leads to multiple versions of `iris.R` of indeterminate relatedness (Figure \ref{fig:diy-vs-git}A). In collaborative settings based on email distribution, the original file swiftly becomes part of a complicated phylogeny that no amount of "Track changes" and good intentions can resolve (Figure \ref{fig:diy-vs-git}B).
